---
title: "Visualizations"
format: 
  html:
    page-layout: full
    theme: cosmo
    toc: true
    toc-title: "Contents"
    embed-resources: true
    standalone: true
editor: 
  markdown: 
    wrap: 72
---

### Figure 1: Movie Profitability vs. Worldwide Gross

```{r}
#| echo: false
#| message: false
#| warning: false
library(dplyr)
library(tidyverse)
library(reticulate)
library(ggplot2)
```

```{r}
#| echo: false
#| message: false
#| warning: false
movies <- read.csv("/Users/noranowicki/MATH-244-Final-Project-Website/HollywoodMovies.csv")
movies <- movies %>%
  mutate(BOAvgOpenWeekend = BOAvgOpenWeekend / 1000000)

movies <- movies %>% 
  drop_na()
movies <- movies %>% 
  mutate(across(where(is.character), ~ na_if(., ""))) %>% 
  drop_na()
```

```{r}
#| echo: false
#| message: false
#| warning: false
movies <- movies |>
  filter(Profitability <= 2000, WorldGross <= 1000) 
#filter out profitability <= 2000, and worldgross <= 1000 in order to remove extreme outliers

top5_genres <- movies |>
  count(Genre, sort = TRUE) |>  # Count occurrences of each genre
  slice_max(n, n = 5) |>         # Take top 5
  pull(Genre)                     

# Filter data to only include top 5 genres
movies_top5 <- movies |>
  filter(Genre %in% top5_genres)

# Visualize profitability and world gross with genre as the points
ggplot(data = movies_top5, aes(x = WorldGross, y = Profitability, color = Genre)) + geom_point() + geom_smooth(method = "lm", se = FALSE) + labs(
    title = "Movie Profitability vs. Worldwide Gross",
    x = "Worldwide Gross (in millions $)",
    y = "Profitability (in millions $)",
    color = "Film Genre"
  ) +
  theme_minimal()
```

### Figure 2: Audience Score vs. Worldwide Gross

```{r}
#| echo: false
#| message: false
#| warning: false
ggplot(data = movies_top5, aes(x = AudienceScore, y = WorldGross, color = Genre)) + geom_point() + geom_smooth(method = "lm", se = FALSE) + facet_wrap(~ Genre, scales = "free", ncol = 3) + labs(
    title = "Audience Score vs. Worldwide Gross",
    x = "Audience Score (%)",
    y = "Worldwide Gross (in millions $)"
  ) +
  theme_minimal()
```

### Figure 3: Distribution of World Gross by Rotten Tomatoes and Audience Scores

```{r}
#| echo: false
#| message: false
#| warning: false
critic_review <- pivot_longer(movies, 
                        cols = c(AudienceScore, RottenTomatoes),
                        names_to = "group",
                        values_to = "value")

ggplot(data = critic_review,
       mapping = aes(x = group, y = value, fill = group)) +
  geom_boxplot() +
  labs(title = "Distribution of World Gross by Rotten Tomatoes and Audience Scores",
       x = "Critic Scores (percent)", 
       y = "World Gross (million)") +
  theme_minimal()
```
### Figure 4: Number of Theaters Showing Movie vs. Opening Weekend Revenue

```{r}
#| echo: false
#| message: false
#| warning: false
ggplot(data = movies,
       mapping = aes(x = TheatersOpenWeek, y = OpeningWeekend)) +
  geom_point() +
  geom_smooth(method = "glm", 
              formula = y ~ x,
              method.args = list(family = gaussian(link = "log")),
              color = "red", se = FALSE) +
  labs(title = "Number of Theaters Showing Movie vs. Opening Weekend Revenue",
       x = "Number of Theaters Showing Movie",
       y = "Opening Weekend Revenue (in millions $)") +
  theme_minimal()
```
## Clustering Model Visualization

### Figure 5: World Gross Distribution by Budget Cluster

```{r}
#| echo: false
#| message: false
#| warning: false
budget_data <- data.frame(Budget = movies$Budget)

set.seed(123)
kmeans_result <- kmeans(budget_data, centers = 5)
kmeans_result$centers

movies$Cluster <- as.factor(kmeans_result$cluster)

budget_ranges <- movies %>%
  group_by(Cluster) %>%
  summarise(
    Count = n(),
    Min_Budget = min(Budget, na.rm = TRUE),
    Max_Budget = max(Budget, na.rm = TRUE),
    Mean_Budget = mean(Budget, na.rm = TRUE),
    Budget_Range = paste("$", round(Min_Budget, 0), "-", round(Max_Budget, 0))
  )

print(budget_ranges)
print(kmeans_result$centers)

cluster_means <- movies %>%
  group_by(Cluster) %>%
  summarise(mean_opening = mean(OpeningWeekend, na.rm = TRUE)) %>%
  arrange(mean_opening)


movies$Cluster <- factor(movies$Cluster, 
                         levels = cluster_means$Cluster[order(cluster_means$mean_opening)])
cluster_graph <- ggplot(data = movies, aes(x = Cluster, y = WorldGross, fill = Cluster)) +
  geom_boxplot() + labs(title = "World Gross Distribution by Budget Cluster",
       x = "Budget Cluster",
       y = "Worldwide Gross (in millions $)") +
  stat_summary(fun = mean, geom = "point", shape = 18, size = 4, color = "black") +
  theme_minimal()
cluster_graph
```

## Multilinear Regression Models

### Profitability Model

```{r}
#| echo: false
#| message: false
#| warning: false
m1 <- lm(Profitability ~ RottenTomatoes + AudienceScore + TheatersOpenWeek + Genre + BOAvgOpenWeekend, data = movies_top5)
summary(m1)
```
### World Gross Model

```{r}
#| echo: false
#| message: false
#| warning: false
m2 <- lm(WorldGross ~ RottenTomatoes + AudienceScore + TheatersOpenWeek + Genre + BOAvgOpenWeekend, data = movies_top5)
summary(m2)
```

